\documentclass{article}
\usepackage{enumerate}
\usepackage[margin=1in]{geometry}
\usepackage[pdftex]{graphicx}
\usepackage{hyperref}

\begin{document}

\begin{center}
{\Huge {Math 502A}}

\vspace{0.2in}

{\Large {Classwork Assignment 2}}
\end{center}

\vspace{0.1in}

\section{Socks Problem Part 1}

Suppose that two socks are drawn at random without replacement from a drawer containing $b \geq 2$ black socks and $w \geq 2$ white socks. The socks are otherwise identical.

\begin{enumerate}[(a)]
\item What is the probability of first drawing a black sock, and then a white sock?
\item What is the probability of drawing a black pair?
\item What is the probability of drawing a pair of any color?
\end{enumerate}

\section{Socks Problem Part 2}

Suppose that four socks are drawn at random without replacement from a drawer containing $b \geq 2$ black socks and $w \geq 2$ white socks. The socks are otherwise identical.

\begin{enumerate}[(a)]
\item What is the probability of drawing the exact sequence black, white, black, white?
\item What is the probability of drawing exactly one black pair and one white pair?
\end{enumerate}

\section {World Series}

The World Series is a series of up to seven games played between the champions of Major League Baseball's American League and National League. Under normal circumstances, the first two games are played at Team A's home stadium, the next three are played at Team B's home stadium, and the final two are played at Team A's home stadium. Once a team has won four games, that team wins the World Series and any remaining games are not played. Using 50 years of data from 1969-2018, we estimate that the home team has a 59\% chance of winning any given World Series game. We also assume that the result of each game is independent of the result of the previous game(s). 

\begin{enumerate}[(a)]
\item In the 2019 World Series, the home team lost each of the seven games. \href{https://www.theringer.com/mlb-playoffs/2019/10/31/20942186/nationals-astros-world-series-home-field-advantage-history}{One analysis} estimated that the probability of this happening was approximately 0.0019. Show that their calculations are correct, given the assumptions in the introduction to the problem.
\item What is the probability that Team A sweeps the World Series (wins each of the first four games)?
\item Given that Team B wins the first two games, what is the probability that it wins the World Series without playing another game at Team A's home stadium?

\end{enumerate} 

\end{document}